Queue Aware Precoder Design for Space Frequency Resource Allocation

### 2014-08-21 Report/primal_algorithm.tex
Modifications made for the convergence

The primal decomposition approach is modeled by having a master controller, which controls the resources allocated to each \acp{BS} based on which the optimization is carried out locally at each \ac{BS}. In this scheme, the problem described in \eqref{eqn-9} is decomposed in a way that the precoders intended for the users associated with each \ac{BS} are designed locally with the additional constraint on the interference caused by the transmission to the neighbouring \ac{BS} users. The interference thresholds are set by the centralized controller for each data stream of the users in the system, which needs to be satisfied by the neighbouring \acp{BS} while designing the precoders.

@@

In order to decouple the precoder design, \acp{BS} use the fixed interference levels set by the centralized controller in the \ac{SINR} expression \eqref{eq:SINR-primal} and additional interference constraints to limit the interference caused by the \ac{BS} \me{b} to the neighbouring users \me{\pr{k} \notin \mc{U}_b} is given by \eqref{eq-primal-constr}. Using the above constraints and approximations, the precoder design problem for a \ac{BS} \me{b} using the fixed interference level is given by
\begin{IEEEeqnarray}{rCl}\label{primal-problem}
\underset{\substack{\mvec{m}{l,k,n},p_{l,k,n},\\q_{l,k,n},\beta_{l,k,n}}}{\text{minimize}} & \quad & \| \tilde{\mbf{v}}_{b} \|_q \IEEEyessubnumber \\
\text{subject to} & \quad & \bar{\gamma}_{l,k,n} \leq \dfrac{p_{l,k,n}^2 + q_{l,k,n}^2}{\beta_{l,k,n}} \IEEEyessubnumber \label{eqn-sg-b} \\
& \quad & N_0 + \rho_{l,k,n} + \sum_{\pr{b} \in \tilde{\mc{B}}_{b}} \chi_{l,\pr{b},k,n} \leq \beta_{l,k,n} \IEEEyessubnumber \label{eqn-sg-d} \\
& \quad & \eqref{eqn-4.3}, \eqref{eqn-8}, \text{ and } \eqref{eq-primal-constr}, \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{p_{l,k,n}, q_{l,k,n}, \bar{\gamma}_{l,k,n}}, and \me{\rho_{l,k,n}} are as defined in \eqref{eqn-wsrm-expr}, \eqref{eq:SINR-primal} and \eqref{eqn-rho} respectively. The weighted deviation vector \me{\tilde{\mbf{v}}_{b}} stack the weighted deviation metric of users belonging to the \ac{BS} \me{b} as the component elements as discussed earlier.

The local optimization problem solved at the \acp{BS} are coordinated by exchanging minimal information through the backhaul link across the coordinating \acp{BS} to design the optimum set of precoders at each \ac{BS}. The master problem, which determines the interference level for each \ac{BS} is obtained by solving the subgradient of the original problem \cite{palomar2006tutorial} and \cite{pennanen2011decentralized}. In order to obtain the dual variables corresponding to the coupling constraints, partial Lagrangian of the decentralized problem involving the coupling variable \me{\chi_{l,b,\pr{k},n}} is solved. The Lagrangian of the problem outlined in \eqref{primal-problem} is given by
\begin{IEEEeqnarray}{rCl}\label{lagr-primal}
\underset{\substack{\mvec{m}{l,k,n},p_{l,k,n},\\q_{l,k,n},\beta_{l,k,n},\mbfa{\mu}^{(b)}}}{\text{minimize}} &\quad& \|\tilde{\mbf{v}}_{b}\|_q + \sum_{k \in \mc{U}_{b}} \sum_{l = 1}^L \mu^{(b)}_{l,k,n} \left ( \beta_{l,k,n} - N_0 - \rho_{l,k,n} - \sum_{\pr{b} \in \tilde{\mc{B}}_{b}} \chi_{l,\pr{b},k,n} \right ) \nonumber \\
&\quad& + \sum_{\pr{k} \notin \mc{U}_b} \sum_{\pr{l} = 1}^L \mu^{(b)}_{\pr{l},\pr{k},n} \left ( \chi_{\pr{l},b,\pr{k},n} - \sum_{k \in \mc{U}_{b}} \text{tr} \left ( \mvec{w}{\pr{l},\pr{k},n}^H \mvec{H}{b,\pr{k},n} \mvec{M}{k,n} \mvec{M}{k,n}^H \mvec{H}{b,\pr{k},n}^H \mvec{w}{\pr{l},\pr{k},n} \, \right ) \right ) \IEEEyessubnumber \\
\text{subject to}&\quad& \eqref{eqn-4.3}, \eqref{eqn-8}, \text{and} \, \eqref{eqn-sg-b} \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{\mu^{(b)}_{l,k,n}} represent the dual variable for the constraint \eqref{eqn-sg-d} and \me{\mu^{(b)}_{\pr{l},\pr{k},n}} denote the dual variable for the constraint \eqref{eq-primal-constr} respectively. In order to solve the master problem, the dual variables of the \acp{BS}, which are linked by the interference constraint, need to be exchanged between the \acp{BS} \me{b} and \me{\pr{b}} only. For example, in order to find the interference threshold \me{\chi_{l,\pr{b},k,n}} for the \me{\ith{(i+1)}} iteration, the dual variables and the interference threshold levels of the \me{\ith{(i)}} iteration are exchanged to update \me{\chi_{l,\pr{b},k,n}}. The subgradient update for \me{\chi_{l,\pr{b},k,n}} is given by
\begin{equation}
\chi_{l,\pr{b},k,n}(i + 1) = \left [ \; \chi_{l,\pr{b},k,n}(i) - \sigma(i) \, s^{(\pr{b})}_{l,k,n}(i) \; \right ]^+, \; \forall \pr{b} \in \mc{B}, \forall k \notin \mc{U}_{b}
\label{eqn-primal-sg}
\end{equation}
where \me{\sigma} is the positive step-size which determines the convergence behaviour, and \me{s^{(\pr{b})}_{l,k,n}} is the global subgradient evaluated at the point \me{\chi_{l,\pr{b},k,n}}. Since the inter-cell interference term \me{\chi_{l,\pr{b},k,n}} couples exactly two \acp{BS}, \me{b} and \me{\pr{b}}, the global subgradient can be expressed as \me{s^{(\pr{b})}_{l,k,n}(i) = \mu^{(b)}_{l,k,n}(i) - \mu^{(\pr{b})}_{l,k,n}(i), \, \forall \pr{b} \in \tilde{\mc{B}}_b, \forall k \notin \mc{U}_{b}}.

>>>>

The primal decomposition approach is modeled by having a master controller, which controls the resources allocated to each \acp{BS} based on which the optimization is carried out locally at each \ac{BS}. In this scheme, the problem described in \eqref{eqn-9} is decomposed in a way that the precoders intended for the users associated with each \ac{BS} are designed locally with the additional constraint on the interference caused by the transmission to the neighboring \ac{BS} users. The interference thresholds are set by the centralized controller for each data stream of the users in the system, which needs to be satisfied by the neighboring \acp{BS} while designing the precoders.

@@

In order to decouple the precoder design, \acp{BS} use the fixed interference levels set by the centralized controller in the \ac{SINR} expression \eqref{eq:SINR-primal} and additional interference constraints to limit the interference caused by the \ac{BS} \me{b} to the neighboring users \me{\pr{k} \notin \mc{U}_b} is given by \eqref{eq-primal-constr}. Using the above constraints and approximations, the precoder design problem for a \ac{BS} \me{b} using the fixed interference level is given by
\begin{IEEEeqnarray}{rCl}\label{primal-problem}
\underset{\substack{\mvec{m}{l,k,n},p_{l,k,n},\\q_{l,k,n},\beta_{l,k,n}}}{\text{minimize}} & \quad & \| \tilde{\mbf{v}}_{b} \|_q \IEEEyessubnumber \\
\text{subject to} & \quad & \bar{\gamma}_{l,k,n} \leq \dfrac{p_{l,k,n}^2 + q_{l,k,n}^2}{\beta_{l,k,n}} \IEEEyessubnumber \label{eqn-sg-b} \\
& \quad & N_0 + \rho_{l,k,n} + \sum_{\pr{b} \in \tilde{\mc{B}}_{b}} \chi_{l,\pr{b},k,n} \leq \beta_{l,k,n} \IEEEyessubnumber \label{eqn-sg-d} \\
& \quad & \eqref{eqn-4.3}, \eqref{eqn-8}, \text{ and } \eqref{eq-primal-constr}, \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{p_{l,k,n}, q_{l,k,n}, \bar{\gamma}_{l,k,n}}, and \me{\rho_{l,k,n}} are as defined in \eqref{eqn-wsrm-expr}, \eqref{eq:SINR-primal} and \eqref{eqn-rho} respectively. The weighted deviation vector \me{\tilde{\mbf{v}}_{b}} stack the weighted deviation metric of users belonging to the \ac{BS} \me{b} as the component elements as discussed earlier.

The local optimization problem solved at the \acp{BS} are coordinated by exchanging minimal information through the backhaul link across the coordinating \acp{BS} to design the optimum set of precoders at each \ac{BS}. The master problem, which determines the interference level for each \ac{BS} is obtained by solving the subgradient of the original problem \cite{palomar2006tutorial} and \cite{pennanen2011decentralized}. In order to obtain the dual variables corresponding to the coupling constraints, partial Lagrangian of the decentralized problem involving the coupling variable \me{\chi_{l,b,\pr{k},n}} is solved. The Lagrangian of the problem outlined in \eqref{primal-problem} is given by
\begin{IEEEeqnarray}{rCl}\label{lagr-primal}
\underset{\substack{\mvec{m}{l,k,n},p_{l,k,n},\\q_{l,k,n},\beta_{l,k,n},\mbfa{\mu}^{(b)}}}{\text{minimize}} &\quad& \|\tilde{\mbf{v}}_{b}\|_q + \sum_{k \in \mc{U}_{b}} \sum_{l = 1}^L \mu^{(b)}_{l,k,n} \left ( \beta_{l,k,n} - N_0 - \rho_{l,k,n} - \sum_{\pr{b} \in \tilde{\mc{B}}_{b}} \chi_{l,\pr{b},k,n} \right ) \nonumber \\
&\quad& + \sum_{\pr{k} \notin \mc{U}_b} \sum_{\pr{l} = 1}^L \mu^{(b)}_{\pr{l},\pr{k},n} \left ( \chi_{\pr{l},b,\pr{k},n} - \sum_{k \in \mc{U}_{b}} \text{tr} \left ( \mvec{w}{\pr{l},\pr{k},n}^H \mvec{H}{b,\pr{k},n} \mvec{M}{k,n} \mvec{M}{k,n}^H \mvec{H}{b,\pr{k},n}^H \mvec{w}{\pr{l},\pr{k},n} \, \right ) \right ) \IEEEyessubnumber \\
\text{subject to}&\quad& \eqref{eqn-4.3}, \eqref{eqn-8}, \text{and} \, \eqref{eqn-sg-b} \IEEEyessubnumber
\end{IEEEeqnarray}
where \me{\mu^{(b)}_{l,k,n}} represent the dual variable for the constraint \eqref{eqn-sg-d} and \me{\mu^{(b)}_{\pr{l},\pr{k},n}} denote the dual variable for the constraint \eqref{eq-primal-constr} respectively. In order to solve the master problem, the dual variables of the \acp{BS}, which are linked by the interference constraint, need to be exchanged between the \acp{BS} \me{b} and \me{\pr{b}} only. For example, in order to find the interference threshold \me{\chi_{l,\pr{b},k,n}} for the \me{\ith{(i+1)}} iteration, the dual variables and the interference threshold levels of the \me{\ith{(i)}} iteration are exchanged to update \me{\chi_{l,\pr{b},k,n}}. The subgradient update for \me{\chi_{l,\pr{b},k,n}} is given by
\begin{equation}
\chi_{l,\pr{b},k,n}(i + 1) = \left [ \; \chi_{l,\pr{b},k,n}(i) - \sigma(i) \, s^{(\pr{b})}_{l,k,n}(i) \; \right ]^+, \; \forall \pr{b} \in \mc{B}, \forall k \notin \mc{U}_{b}
\label{eqn-primal-sg}
\end{equation}
where \me{\sigma} is the positive step-size which determines the convergence behavior, and \me{s^{(\pr{b})}_{l,k,n}} is the global subgradient evaluated at the point \me{\chi_{l,\pr{b},k,n}}. Since the inter-cell interference term \me{\chi_{l,\pr{b},k,n}} couples exactly two \acp{BS}, \me{b} and \me{\pr{b}}, the global subgradient can be expressed as \me{s^{(\pr{b})}_{l,k,n}(i) = \mu^{(b)}_{l,k,n}(i) - \mu^{(\pr{b})}_{l,k,n}(i), \, \forall \pr{b} \in \tilde{\mc{B}}_b, \forall k \notin \mc{U}_{b}}.

### 2014-08-21 Report/primal_approach_appendix.tex
modified for review
Modifications made for the convergence

To obtain the next interference iterate at each \ac{BS}, the locally evaluated dual variables are exchanged among the \acp{BS} in the set \me{\mc{B}} in order to obtain the next interference vector in a distributed manner. Once we obtain the dual variables from all the \acp{BS}, the subgradients relevant to the \ac{BS} \me{b_k} are evaluated by taking the difference between the two \acp{BS} associated with each interference value, \textit{i.e}, \me{s^{\set{b_k}(i)}_{l,k,n,b} = \mu^{\set{b_k}}_{l,k,n} - \mu^{\set{b}}_{l,k,n}}. With the newly estimated subgradient value \me{s^{\set{b_k}(i)}_{l,k,n,b}}, the interference terms corresponding to the \ac{BS} \me{b_k} are updated using \eqref{primal-sg-update}. The algorithmic representation of the \ac{PD} approach is detailed in Algorithm. \ref{algo-2}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
 update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}} \;
 initialize the interference threshold \me{\zeta_{l,k,n,b}^{\set{0}} \forall b \in \mc{B}, \forall k \in \bar{\mc{U}}_{b_k}, \forall l,n} \;
 for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
 \Repeat{convergence or \me{i \geq I_{\max}}}{
    initialize \me{j=0} \;
    \Repeat{convergence or \me{j \geq J_{\max}}}{
        solve for the transmit precoders \me{\mvec{m}{l,k,n}} and dual variables \me{\mu^{\set{b}}_{l,k,n}} using \eqref{eqn-primal-2} \;
        exchange \me{\mu^{\set{b}}_{l,k,n}} across the coordinating \acp{BS} in \me{\mc{B}} \;
        update \me{\zeta^{\set{b}(j+1)}_{l,k,n,b}} using \eqref{primal-sg-update} locally \;
        \me{j = j + 1} \;
    }
    update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} by exchanging the recent precoders \me{\mvec{m}{l,k,n}} \;
    exchange the receive precoders \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
    update \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} with the recent precoders using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or) \;
    update \me{\tilde{\epsilon}_{l,k,n}} with the recent precoders using \eqref{eqn-mse-2.3} with equality for the \ac{MSE} formulation approach \;
    $i = i + 1$ \;
  }
 \caption{Decentralization via Primal Decomposition for \acs{JSFRA} scheme}
  \label{algo-2}
\end{algorithm}

>>>>

To obtain the next interference iterate at each \ac{BS}, the locally evaluated dual variables are exchanged among the \acp{BS} in the set \me{\mc{B}} in order to obtain the next interference vector in a distributed manner. Once we obtain the dual variables from all the \acp{BS}, subgradients relevant to the \ac{BS} \me{b_k} are evaluated by taking the difference between the two \acp{BS} associated with each interference value, \textit{i.e}, \me{s^{\set{b_k}(i)}_{l,k,n,b} = \mu^{\set{b_k}}_{l,k,n} - \mu^{\set{b}}_{l,k,n}}. With the newly estimated subgradient value \me{s^{\set{b_k}(i)}_{l,k,n,b}}, the interference terms corresponding to the \ac{BS} \me{b_k} are updated using \eqref{primal-sg-update}. The algorithmic representation of the \ac{PD} approach is detailed in Algorithm. \ref{algo-2}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
 update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}} \;
 initialize the interference threshold \me{\zeta_{l,k,n,b}^{\set{0}} \forall b \in \mc{B}, \forall k \in \bar{\mc{U}}_{b_k}, \forall l,n} \;
 for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
 \Repeat{convergence or \me{i \geq I_{\max}}}{
    initialize \me{j=0} \;
    \Repeat{convergence or \me{j \geq J_{\max}}}{
        solve for the transmit precoders \me{\mvec{m}{l,k,n}} and dual variables \me{\mu^{\set{b}}_{l,k,n}} using \eqref{eqn-primal-2} \;
        exchange \me{\mu^{\set{b}}_{l,k,n}} across the coordinating \acp{BS} in \me{\mc{B}} \;
        update \me{\zeta^{\set{b}(j+1)}_{l,k,n,b}} using \eqref{primal-sg-update} locally \;
        \me{j = j + 1} \;
    }
    update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} by exchanging the recent precoders \me{\mvec{m}{l,k,n}} \;
    exchange the receive precoders \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
    update \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} with the recent precoders using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or) \;
    update \me{\tilde{\epsilon}_{l,k,n}} with the recent precoders using \eqref{eqn-mse-2.3} with equality for the \ac{MSE} formulation approach \;
    $i = i + 1$ \;
  }
 \caption{Decentralization via Primal Decomposition for \acs{JSFRA} scheme}
  \label{algo-2}
\end{algorithm}

### 2014-08-21 Report/simulation_intro.tex
Modifications made for the convergence

The simulations carried out in this work considered the path loss varying uniformly across all users in the system with the channels drawn from the i.i.d samples. The queues are generated based on the poisson process with the average values specified in each section presented.

>>>>

The simulations carried out in this work considered the path loss varying uniformly across all users in the system with the channels drawn from the \textit{i.i.d} samples. The queues are generated based on the Poisson process with the average values specified in each section presented.

### 2014-08-21 Report/sub_channel_wsrm.tex
Modifications made for the convergence

The proposed \acf{QM} \ac{SRA} scheme decouples the problem by fixing the power across each sub-channel to a constant value \me{P_{\max,n}} as compared to the global power constraint defined by \eqref{eqn-4.3}. In contrast to the decomposition based approach for the sub-channel wise resource allocation, where the primal/dual variables are exchanged, this method requires the update on the number of queued bits before each sub-channel wise optimization. The number of queued bits for each user are updated by the difference between the total number of queued bits present during the current slot to the total number of bits that are guaranteed by the earlier sub-channel allocations for the same slot as
\begin{equation}
Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{j = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}
\label{eqn-weight}
\end{equation}
where \me{Q_{k,n}} is the total number of queued bits used in the optimization problem carried out for the sub-channel \me{n}. In the expression \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,j}} is the rate or guaranteed bits allocated over the sub-channel \me{j}. The current scheme is very sensitive to the order in which the sub-channels are selected for the optimization problem. The algorithmic representation of the \acf{QM} \ac{SRA} scheme is shown in Algorithm \ref{algo-5}
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}}}
 \KwIn{permute \me{\mathcal{N} \rightarrow \tilde{\mathcal{N}}}}
 \For{\me{n \leftarrow 1 } \KwTo \me{N}}{
 update \me{Q_{k,n}} using \eqref{eqn-weight} and let \me{\hat{n} = \tilde{\mathcal{N}}(n)}. \;
 \KwOut{\me{\mvec{m}{l,k,\hat{n}}} and \me{\mvec{w}{l,k,\hat{n}} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0}, \me{j=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,\hat{n}}} randomly satisfying per sub-channel power constraint \me{P_{\max,\hat{n}}}}
 update \me{\mvec{w}{l,k,\hat{n}}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,\hat{n}}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,\hat{n}}}.\;
 \Repeat{Queue convergence or \me{j \geq J_{\max}}}{
 \Repeat{\ac{SCA} convergence or \me{i \geq I_{\max}}}{
 solve for the transmit precoders \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-9} \;
 update the constraint set \eqref{eqn-8} with \me{\tilde{p}_{l,k,\hat{n}}}, \me{\tilde{q}_{l,k,\hat{n}}} and \me{\tilde{\beta}_{l,k,\hat{n}}} using \eqref{eqn-wsrm-expr} with the precoders \me{\mvec{m}{l,k,\hat{n}}} obtained from the previous step. \;
 $i = i + 1$. \;
 }
 update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}}. \;
 $j = j + 1$. \;
 }
 }
 \caption{Algorithm of \acs{SRA} scheme}
 \label{algo-5}
\end{algorithm}

>>>>

The proposed \acf{QM} \ac{SRA} scheme decouples the problem by fixing the power across each sub-channel to a constant value \me{P_{\max,n}} as compared to the global power constraint defined by \eqref{eqn-4.3}. In contrast to the decomposition based approach for the sub-channel wise resource allocation, where the primal/dual variables are exchanged, this method requires the update on the number of queued bits before each sub-channel wise optimization. The total number of queued bits for each user are updated by the difference between the total number of queued bits present during the current slot to the total number of bits that are guaranteed by the earlier sub-channel allocations for the same slot as
\begin{equation}
Q_{k,n} = \max{\Big \lbrace Q_k - \sum_{j = 1}^{n-1} \, \sum_{l = 1}^{L} \, t_{l,k,j} ,0 \Big \rbrace }, \; \forall \; k \in \mathcal{U}
\label{eqn-weight}
\end{equation}
where \me{Q_{k,n}} is the total number of queued bits used in the optimization problem carried out for the sub-channel \me{n}. In the expression \eqref{eqn-weight}, \me{Q_k} denotes the total number of queued bits waiting to be transmitted for the user \me{k} during the current slot and \me{t_{l,k,j}} is the rate or guaranteed bits allocated over the sub-channel \me{j}. The current scheme is very sensitive to the order in which the sub-channels are selected for the optimization problem. The algorithmic representation of the \acf{QM} \ac{SRA} scheme is shown in Algorithm \ref{algo-5}
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}}}
 \KwIn{permute \me{\mathcal{N} \rightarrow \tilde{\mathcal{N}}}}
 \For{\me{n \leftarrow 1 } \KwTo \me{N}}{
 update \me{Q_{k,n}} using \eqref{eqn-weight} and let \me{\hat{n} = \tilde{\mathcal{N}}(n)}. \;
 \KwOut{\me{\mvec{m}{l,k,\hat{n}}} and \me{\mvec{w}{l,k,\hat{n}} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0}, \me{j=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,\hat{n}}} randomly satisfying per sub-channel power constraint \me{P_{\max,\hat{n}}}}
 update \me{\mvec{w}{l,k,\hat{n}}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,\hat{n}}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,\hat{n}}}.\;
 \Repeat{Queue convergence or \me{j \geq J_{\max}}}{
 \Repeat{\ac{SCA} convergence or \me{i \geq I_{\max}}}{
 solve for the transmit precoders \me{\mvec{m}{l,k,\hat{n}}} using \eqref{eqn-9} \;
 update the constraint set \eqref{eqn-8} with \me{\tilde{p}_{l,k,\hat{n}}}, \me{\tilde{q}_{l,k,\hat{n}}} and \me{\tilde{\beta}_{l,k,\hat{n}}} using \eqref{eqn-wsrm-expr} with the precoders \me{\mvec{m}{l,k,\hat{n}}} obtained from the previous step. \;
 $i = i + 1$. \;
 }
 update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}}. \;
 $j = j + 1$. \;
 }
 }
 \caption{Algorithm of \acs{SRA} scheme}
 \label{algo-5}
\end{algorithm}
